The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the last glacial maximum

### 2013-06-11 cordillera-climate.tex
Empty sections coming soon...
Added more todonotes in figures
Implement Arjen comments
Trivial comments implemented in the text; others as todo notes.
Throw in all the modelling references
And expand the introduction.
Remove technical note
Change the title

% Extra packages
%\usepackage{color}
%\usepackage{hyperref}

% All floats at the end of the manuscripts
\usepackage{endfloat}

% Add to-do notes
\usepackage{todonotes}
\newcommand{\missingref}[0]{\todo[color=cyan]{Need ref.}}

@@

\title{Choosing climate forcing for numerical simulations of the Cordilleran ice sheet}
\runningtitle{Cordilleran ice sheet climate forcing}

@@

% ----------------------------------------------------------------------
\begin{abstract}
We present an ensemble of numerical simulations of the former Cordilleran ice sheet forced by present-day climatologies from five different datasets. Surface air temperature and precipitation rates from the NCEP/NCAR reanalysis, the Climate Forecast System Reanalysis, the ERA-Interim reanalysis and the North American Regional Reanalysis are used to force the ice sheet model PISM. Glacial conditions are mimicked by applying constant temperature offsets over the entire modelling domain, and a positive degree-day model is used to compute surface mass balance. The modelled ice sheet appears highly sensitive to the choice of climate forcing. Best results were obtained from the North American Regional Reanalysis, a high-resolution regional reanalysis which assimilates precipitation.
\end{abstract}
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
\conclusions  %% \conclusions[modified heading if necessary]
\label{sec:conclusion}
% ----------------------------------------------------------------------

>>>>

% Extra packages
\usepackage[colorlinks,citecolor=blue]{hyperref}
\usepackage{framed}

% Recognize utf-8 special characters
\usepackage[utf8]{inputenc}

% All floats at the end of the manuscripts
%\usepackage{endfloat}

% Add to-do notes and enlarge right margin
\usepackage{todonotes}
\usepackage[left=54pt, top=81pt, textwidth=398pt, marginparsep=11pt, marginparwidth=93pt, textheight=625pt, footskip=30pt]{geometry}
\newcommand{\needref}[0]{\todo[color=cyan]{Reference needed}}
\newcommand{\arjen}[2][]{\todo[color=lime,{#1}]{\textbf{Arjen:} #2}}
\newcommand{\constantine}[2][]{\todo[color=yellow,{#1}]{\textbf{Constantine:} #2}}
\newcommand{\qiong}[2][]{\todo[color=pink,{#1}]{\textbf{Qiong:} #2}}
\newcommand{\ask}[2][]{\todo[color=lightgray,{#1}]{\textbf{Julien:} #2}}

% Personal shortcuts
\newcommand{\degC}[0]{\,\unit{\degree C} }
\newcommand{\masl}[0]{\,\unit{m a.s.l.} }

@@

\title{The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the last glacial maximum}
\runningtitle{Climate forcing for Cordilleran ice sheet simulations}

@@

% ----------------------------------------------------------------------
\begin{abstract}
\todo{This abstract is preliminary. I will rewrite it when I am done with the rest}
We present an ensemble of numerical simulations of the former Cordilleran ice sheet forced by present-day climatologies from five different datasets. Surface air temperature and precipitation rates from the NCEP/NCAR reanalysis, the Climate Forecast System Reanalysis, the ERA-Interim reanalysis and the North American Regional Reanalysis are used to force the ice sheet model PISM. Glacial conditions are mimicked by applying constant temperature offsets over the entire modelling domain, and a positive degree-day model is used to compute surface mass balance. The modelled ice sheet appears highly sensitive to the choice of climate forcing. Best results were obtained from the North American Regional Reanalysis, a high-resolution regional reanalysis which assimilates precipitation.
\end{abstract}
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
\conclusions  %% \conclusions[modified heading if necessary]
\label{sec:conclusion}
\emph{Coming soon...}
% ----------------------------------------------------------------------
